### 2015-07-06 narrative/data-description.tex
more refs added

\paragraph{State of the art:}
Our current data annotation techniques demonstrated in
ADIOS~\cite{lofstead:2009:ipdps} implements a binary-packed data format that
allows data characteristics such as min, max and index to be wrapped around
data chunks. A direct benefit is that each data chunk can be operated upon
independently and I/O concurrently can be maximized. We will build upon this
capability and further augment the format to express data utility.  Recently
DAMSEL~\cite{damsel} provides a rich metadata representation and management
layer that captures the relationship between data blocks for scientific
applications.  This allows application data to be mapped to storage system
efficiently, without overburdening users to managing complex data model, such
as AMR, from the user space. However, the aspect of data importance hasn't been
explored, which we believe will be important for exascale storage solutions.
{\color{red}\bf there must be other work in this area, and we need to get more
references}

>>>>

\paragraph{State of the art:}
Our current data annotation techniques demonstrated in
ADIOS~\cite{lofstead:2009:adaptible} implements a binary-packed data format that
allows data characteristics such as min, max and index to be wrapped around
data chunks. A direct benefit is that each data chunk can be operated upon
independently and I/O concurrently can be maximized. We will build upon this
capability and further augment the format to express data utility.  Recently
DAMSEL~\cite{damsel} provides a rich metadata representation and management
layer that captures the relationship between data blocks for scientific
applications.  This allows application data to be mapped to storage system
efficiently, without overburdening users to managing complex data model, such
as AMR, from the user space. However, the aspect of data importance hasn't been
explored, which we believe will be important for exascale storage solutions.
{\color{red}\bf there must be other work in this area, and we need to get more
references}

### 2015-07-06 narrative/enabling_tech.tex
more refs added

The LWFS philosophy focuses on providing a universal core with additional
semantics and services layered on top or run along side. For this project, the
Sirocco API is much more complex than a standard POSIX call prompting layering
a more user friendly interface on top. Placing a thin, optimized layer as part
of the storage system will offer the kinds of functionality and semantics this
project proposes. From the user perspective, something like the
ADIOS~\cite{lofstead:adaptible} API offers an API nearly as simple as POSIX, but with the
ability to change the actual data transport mechanism without changing the
source code. This affords writing to a single output API while shifting from
writing to a POSIX file system, some middleware like
DataSpaces~\cite{dataspaces}, or some other system like Sirocco all without
changing the source code. ADIOS has proven effective for writing to POSIX file
systems, data staging systems~\cite{predata,dataspaces,nessie}, workflow
systems~\cite{flexpath}, and even nothing through the use of a NULL transport.
Part of this project's goals seeks to understand where the dividing line
between the storage layer shared by all users and middleware being used by a
single or small number of users.

At a similar level as ADIOS, but can be used in conjunction, are tools like
DataSpaces~\cite{dataspaces}. They offer a way to request data set portions
from a one component by the next componet in a data flow. In DataSpaces case,
the data transfer does not have to correspond to the data from a single
process.  Instead, DataSpaces will determine where the data is and issue
requests to pull the data from the source to the sink in an on demand process.

@@

In this project we will extend ADIOS~\cite{lofstead:adaptible} with new APIs and novel
techniques to coordinate with the storage back-end. The key idea is offering
the ability to negotiate with the storage system to agree on the tradeoff
between data quality and response time. We will test our ideas on the next
generation OLCF, SNL/LANL, and NERSC systems.

>>>>

The LWFS philosophy focuses on providing a universal core with additional
semantics and services layered on top or run along side. For this project, the
Sirocco API is much more complex than a standard POSIX call prompting layering
a more user friendly interface on top. Placing a thin, optimized layer as part
of the storage system will offer the kinds of functionality and semantics this
project proposes. From the user perspective, something like the
ADIOS~\cite{lofstead:2009:adaptible} API offers an API nearly as simple as POSIX, but with the
ability to change the actual data transport mechanism without changing the
source code. This affords writing to a single output API while shifting from
writing to a POSIX file system, some middleware like
DataSpaces~\cite{docan:2010:dataspaces}, or some other system like Sirocco all without
changing the source code. ADIOS has proven effective for writing to POSIX file
systems, data staging systems~\cite{zheng:2010:predata,docan:2010:dataspaces,oldfield:2006:nessie}, workflow
systems~\cite{flexpath}, and even nothing through the use of a NULL transport.
Part of this project's goals seeks to understand where the dividing line
between the storage layer shared by all users and middleware being used by a
single or small number of users.

At a similar level as ADIOS, but can be used in conjunction, are tools like
DataSpaces~\cite{docan:2010:dataspaces}. They offer a way to request data set portions
from a one component by the next componet in a data flow. In DataSpaces case,
the data transfer does not have to correspond to the data from a single
process.  Instead, DataSpaces will determine where the data is and issue
requests to pull the data from the source to the sink in an on demand process.

@@

In this project we will extend ADIOS~\cite{lofstead:2009:adaptible} with new APIs and novel
techniques to coordinate with the storage back-end. The key idea is offering
the ability to negotiate with the storage system to agree on the tradeoff
between data quality and response time. We will test our ideas on the next
generation OLCF, SNL/LANL, and NERSC systems.
